Imtiyaaz

### 2022-11-16 src/All variables.Rmd
Update All variables.Rmd

```
```{r}

@@

```
```{r}
corrplot(cor(subset2, use = "complete.obs"), 
         method = "number",
         type = "upper",
         tl.col = "black", 
         tl.srt = 30
         )
```

@@

```{r}
# Obtain performance of MLR model
#fit <- model1$fitted.values
#true <- subset1$Price
#summary_model1 <- eval_results(true, fit)

@@

# Combine all performances into a single output
summary <- rbind(summary_ridge, summary_lasso)
rownames(summary) <- c( "Ridge_model", "LASSO_model" )
colnames(summary)[5] <- "R^2"
knitr::kable(summary, digits = 2)
```

>>>>

@@

```{r}
corrplot(cor(subset2, use = "complete.obs"), 
         method = "number",
         type = "upper",
         tl.col = "black", 
         tl.srt = 30
         )
```

@@

```{r}
# Obtain performance of MLR model
fit <- model1$fitted.values
true <- subset2$pov
summary_model1 <- eval_results(true, fit)

@@

# Combine all performances into a single output
summary <- rbind(summary_model1, summary_ridge, summary_lasso)
rownames(summary) <- c("MLR", "Ridge_model", "LASSO_model" )
colnames(summary)[5] <- "R^2"
knitr::kable(summary, digits = 3)
```
